Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-10-30 manuscript/manuscript.tex
add subsubsections into discussion

\begin{table}[h]
    \centering
    \caption{Demographics and Education Levels by County} \label{tab:connecticut-counties}
    \begin{tabular}{l|cccccccc}
    \hline
    \textbf{CATEGORY} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\ \hline
    Total Population & 944977 & 894465.25 & 182657.5 & 163318.25 & 858678 & 268477.75 & 151218.75 & 116608.75 \\
    RACE &  &  &  &  &  &  &  &  \\
    American Indian and Alaska Native race alone & 0.24 & 0.3075 & 0.2025 & 0.195 & 0.1725 & 0.605 & 0.05 & 0.565 \\
    Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 & 4.005 & 4.12 & 4.675 & 1.3675 \\
    Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 & 13.34 & 5.8175 & 3.1075 & 2.33 \\
    Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 & 0.0225 & 0.025 & 0 & 0.015 \\
    White & 72.6325 & 70.67 & 92.6025 & 88.0875 & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
    Ethnicity &  &  &  &  &  &  &  &  \\
    Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 & 17.885 & 10.5 & 5.4475 & 11.6375 \\
    Average rehospitalization rate in the county &  & 0.1575 & 0.14 & 0.145 & 0.1325 & 0.16 & 0.14 & 0.14 \\
    Education &  &  &  &  &  &  &  &  \\
    Associates & 20.74 & 25 & 27.9225 & 26.46 & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
    Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 & 18.785 & 18.3175 & 23.4075 & 14.595 \\
    Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 & 16.3425 & 15.18 & 17.865 & 9.55 \\
    HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 & 30.565 & 29.46 & 27.03 & 33.5125 \\
    Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 & 9.8875 & 7.7725 & 5.385 & 11.365 \\ \hline
    \end{tabular}
    \end{table}

@@

\subsection{Median Income}
The disparity in median income across the four years highlights economic fluctuations, with 
2020 exhibiting the highest income levels. County-wise analysis indicates stark differences, 
particularly in County 1, which consistently outperforms others. This discrepancy in wealth signifies 
potential disparities in access to resources and opportunities, which can significantly impact health outcomes.

\subsection{Housing Affordability}
The stable trend in the percentage of renters spending 50 percent of their income on rent suggests a 
consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.

\subsection{Rehospitalization Rates}
The absence of significant differences in rehospitalization rates by both county and year indicates 
a consistent healthcare landscape. However, it's crucial to explore the reasons behind this stability to identify 
potential factors contributing to the overall health system's effectiveness.

\subsection{Food Stamps Usage}
Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
faced by residents in these regions. This data aligns with the housing affordability trends, suggesting a potential 
link between financial struggles and reliance on government assistance programs.

\subsection{Uninsured Rates}
County 1's consistently high uninsured rate points towards a significant healthcare accessibility issue, 
possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 
a positive change; understanding the policies or interventions during this period could offer valuable insights into 
effective healthcare reforms.

\subsection{Racial Disparities}
The racial demographics highlight disparities in various counties. County 3's higher percentage of white 
individuals, coupled with County 2, 5, and 1 having the highest black population, points to the need for
targeted interventions addressing racial health inequalities. These disparities might be indicative of 
historical, social, and economic factors influencing the healthcare experiences of different racial groups.

>>>>

\ref{tab:connecticut-counties}

\begin{table}[h]
    \centering
    \caption{Demographics and Education Levels by County} \label{tab:connecticut-counties}
    \begin{tabular}{l|cccccccc}
    \hline
    \textbf{CATEGORY} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\ \hline
    Total Population & 944977 & 894465.25 & 182657.5 & 163318.25 & 858678 & 268477.75 & 151218.75 & 116608.75 \\
    RACE &  &  &  &  &  &  &  &  \\
    American Indian and Alaska Native race alone & 0.24 & 0.3075 & 0.2025 & 0.195 & 0.1725 & 0.605 & 0.05 & 0.565 \\
    Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 & 4.005 & 4.12 & 4.675 & 1.3675 \\
    Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 & 13.34 & 5.8175 & 3.1075 & 2.33 \\
    Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 & 0.0225 & 0.025 & 0 & 0.015 \\
    White & 72.6325 & 70.67 & 92.6025 & 88.0875 & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
    Ethnicity &  &  &  &  &  &  &  &  \\
    Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 & 17.885 & 10.5 & 5.4475 & 11.6375 \\
    Education &  &  &  &  &  &  &  &  \\
    Associates & 20.74 & 25 & 27.9225 & 26.46 & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
    Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 & 18.785 & 18.3175 & 23.4075 & 14.595 \\
    Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 & 16.3425 & 15.18 & 17.865 & 9.55 \\
    HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 & 30.565 & 29.46 & 27.03 & 33.5125 \\
    Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 & 9.8875 & 7.7725 & 5.385 & 11.365 \\ \hline
    \end{tabular}
    \end{table}

@@

There does not appear to be a significant relationship produced over the span of four years between the variables for housing affordability

\subsubsection{Median Income}
The disparity in median income across the four years highlights economic fluctuations, with 
2020 exhibiting the highest income levels. County-wise analysis reveals that county 1 has a significantly 
greater median income than other counties. This discrepancy in wealth signifies potential disparities in 
access to resources and opportunities, which can significantly impact health outcomes.

\subsubsection{Housing Affordability}
The stable trend in the percentage of renters spending 50 percent of their income on rent suggests a 
consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.

\subsubsection{Rehospitalization Rates}
The absence of significant differences in rehospitalization rates by both county and year indicates 
a consistent healthcare landscape. However, it's crucial to explore the reasons behind this stability to identify 
potential factors contributing to the overall health system's effectiveness.

\subsubsection{Food Stamps Usage}
Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
faced by residents in these regions. This data aligns with the housing affordability trends, suggesting a potential 
link between financial struggles and reliance on government assistance programs.

\subsubsection{Uninsured Rates}
County 1's consistently high uninsured rate points towards a significant healthcare accessibility issue, 
possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 
a positive change; understanding the policies or interventions during this period could offer valuable insights into 
effective healthcare reforms.

\subsubsection{Racial Disparities}
The racial demographics highlight disparities in various counties. County 3's higher percentage of white 
individuals, coupled with County 2, 5, and 1 having the highest black population, points to the need for
targeted interventions addressing racial health inequalities. These disparities might be indicative of 
historical, social, and economic factors influencing the healthcare experiences of different racial groups.
